### 2015-11-22 Response/Response 3/response-3.tex

\begin{enumerate}

	\item \reviewF{When discussing the convergence of the \ac{SCA} algorithm (Appendix A-C), the authors claim that the \ac{SCA} algorithm converges because the objective function is strictly decreasing and the minimizer in each iteration is unique. However, this is in general not enough to guarantee the convergence of the whole sequence. Instead, one can only claim that every limit point of the whole sequence is a stationary point, or globally optimal solution if the problem is convex. As an example, simply consider the gradient projection algorithm, where each subproblem is strongly convex and the objective function  is strictly decreasing but the whole sequence may not converge. The authors are referred to Bertsekas'  book: Nonlinear Programming.}

	\vspace{1eM}
	\underline{\textbf{Response:}} We thank the reviewer for pointing out that the sequence of iterates generated by the \ac{SCA} algorithm in each \ac{AO} step need not be convergent. Based on the reviewer's reference to the gradient projection algorithm in Nonlinear Programming textbook, we have realized that our earlier convergence proof is not mathematically rigorous. We apologize for our emphasis on the convergence of iterates in our previous manuscript. As suggested by the reviewer, stationarity of limit points of the whole sequence of iterates is now addressed in Appendix A-D by using the following statements. 
	\begin{itemize}
		\item The sequence of iterates generated by the algorithm is bounded, therefore, we can only claim that there exist at least one subsequence that converges to a limit point of the original sequence.
		\item Using a convergent subsequence of the original sequence of iterates, we then discuss that every limit point is a stationary point of nonconvex problem in Appendix A-D.
	\end{itemize}

@@

	We have made changes in Appendices A-C and A-D to address the concerns raised by the reviewer.

	\vspace{1eM}	
	\item \reviewF{Even under the assumption that the inner loop SCA converges, there are doubts with respect to the convergence of the alternating optimization algorithm described by (54). The authors cite [27] to justify convergence, but it is not straightforward to claim that the algorithmic model considered in this manuscript is the same as in [27]. More specifically, let us consider the variable \eqn{x} (so it is consistent with the authors' notation in Appendix A-D). In the algorithmic model of [27], at iteration \eqn{t+1}, all elements of \eqn{\mbf{x}} are updated simultaneously, based on \eqn{\sol{t}}. But in the authors' model, the update of \eqn{\mbf{x}} is performed in two phases: in the first phase, only the elements of \eqn{\mbf{m}} and \eqn{\mbf{\gamma}} in \eqn{\mbf{x}} are updated based on \eqn{\sol{t}}. In the second phase, the remaining elements of \eqn{\mbf{x}} are updated, i.e. \eqn{\mbf{w}} and \eqn{\mbf{\gamma}}, based on both \eqn{\sol{t}} and the elements that have been updated in the first phase. This is not a trivial difference and thus the direct application of the conclusion from [27] in the current context cannot be taken for granted. Due to the open concerns after several revision rounds, it is recommended to reject the paper.}

	\vspace{1eM}
	\underline{\textbf{Response:}} We understand the reviewer's concern on using [R1] to our problem involving both \ac{SCA} and \ac{AO} updates. In each iteration, the proposed method solves only a subset of optimization variables by keeping others fixed, therefore, we cannot use [R1] directly as suggested by the reviewer. Even though we have revised our convergence proof based on a convergent subsequence without referring to [R1], nevertheless, we clarify our usage of [R1] in our previous manuscript for the convergence of iterates.

	\begin{itemize}
		\item We refer to [R2] for a similar usage of [R1] while discussing the convergence of \ac{AO} method used in designing tight frames by solving matrix nearness problem. The reference [R1] used to discuss the convergence of iterates generated by the \ac{AO} method in [R2] by referring \ac{AO} update as a composition of two sub-algorithms, wherein each sub-algorithm updates only a subset of optimization variables. It has been discussed comprehensively in [R2, Appendices I and II]. In particular, the discussion on referring \ac{AO} as two sub-algorithms is presented in [R2, Appendix I-F].
		\item However, we apologize for the incomplete usage of [R1, Theorem 3.1] in our previous manuscript to claim the convergence of beamformer iterates. In [R1, Theorem. 3.1], it has been shown that if the strict monotonicity of the objective sequence is ensured and the iterates are bounded, then \textit{either the sequence of iterates converges or the accumulation points of \eqn{\{\sol{t}\}} is a continuum}.
		\item Therefore, our previous claim on the guaranteed convergence of iterates is not correct, as pointed out by the reviewer. 
		\item Similar approach of restricting the solution set with a proximal operator to ensure strict monotonicity of the objective sequence is presented in [R1, Section 4] under restrictive mapping section. Therefore, even if we use the discussions in [R1], we can only claim that the sequence of iterates \eqn{\{\sol{t}\}} converges to a continuum of accumulation points, and every limit point is a stationary point.
	\end{itemize}

	We have revised Appendix A-D titled \textit{"Stationarity of Limit Points"} to discuss the convergence of the sequence of iterates. We have revised our claim as every limit point of the sequence of iterates generated by the centralized algorithm is a stationary point.

### 2015-11-22 Response/Response 3/reviewer_response.tex

\title{Reviewers Comments \& Authors Replies}

\date{}
\maketitle

\begin{tabular}{p{1.25in}p{4.25in}}
\textbf{Manuscript No.} & Paper T-SP-18051-2014, submitted to \emph{``IEEE Transactions on Signal Processing"} \\ \\
\textbf{Title} & ``Traffic Aware Resource Allocation Schemes for Multi-Cell MIMO-OFDM Systems" \\ \\
\textbf{Authors} & Ganesh Venkatraman, Antti T\"{o}lli, Markku Juntti, and Le-Nam Tran
\end{tabular}

\vspace{0.35in}
The authors are grateful to the associate editor for being considerate enough to provide us with this additional opportunity to revise and correct our convergence analysis. We thank all the reviewers for their valuable comments on the manuscript, which have been greatly helpful to improve the paper quality. Based on the comments, we have revised our manuscript to ensure that all the reviewers comments are addressed properly and also verified the technical correctness of the convergence proof. We have also modified some parts of text to improve the readability.
\input{additions}

### 2015-11-22 Report/convergence_centralized.tex
updated

The following conditions are required to show the convergence of Algorithm \ref{algo-1}, which is used to solve problems \eqref{eqn-6} and \eqref{eqn-mse-1} in an iterative manner.
\begin{itemize}
\item[(a)] Uniqueness of the minimizer in each step
\item[(b)] Objective function should be bounded below
\item[(c)] Feasible set should be compact
\item[(d)] Sequence of objective values should be strictly decreasing
\end{itemize}
Note that condition (a) is required to ensure strict monotonicity of the objective sequence. Therefore, by using above conditions (a)-(d) along with \cite[Th. 3.14]{rudin1964principles}, we show the convergence objective sequence generated by Algorithm \ref{algo-1}. Then, by using the discussions in \cite{marks1978technical,lanckriet2009convergence,scutari_1}, we show that \reviewF{every limit point of the sequence of iterates generated by the Algorithm \ref{algo-1} is a stationary point of original nonconvex problem formulations in \eqref{eqn-6} and \eqref{eqn-mse-1}}.

Before discussing the convergence analysis, let us consider a generalized formulation for the problems in \eqref{eqn-6} and \eqref{eqn-mse-1} as
\begin{IEEEeqnarray}{RcL} \label{con} \neqsub
\underset{\mx,\my,\mz}{\text{minimize}} &\quad& \hat{f}(\mx,\my,\mz) \eqsub \label{con-obj} \\
\text{subject to} &\quad& h(\mz) - g_0(\mx,\my) \leq 0 \eqsub \label{con-dc} \\
&\quad& g_1(\mx,\my) \leq 0 \eqsub \label{con-cvx-blk} \\
&\quad& g_2(\mx) \leq 0 \eqsub \label{con-cvx}
\end{IEEEeqnarray}
where \me{g_2} and \me{\hat{f}} are convex, \me{h} is linear, and \me{g_0} and \me{g_1} are convex w.r.t either \me{\mx} or \me{\my}, but not jointly convex on both variables. The constraint \eqref{con-dc} corresponds to either \eqref{eqn-6.2} or \eqref{eqn-mse-1.2} and the constraint \eqref{con-cvx-blk} represents to either  \eqref{eqn-6.3} or \eqref{eqn-mse-1.3} correspondingly. Other convex constraints are handled by \eqref{con-cvx} and the feasible set of \eqref{con} is given by 
\iftoggle{single_column}{
\begin{equation}
\mc{F} = \{ \; \mx,\my,\mz \; \big | h(\mz) - g_0(\mx,\my) \leq 0, g_1(\mx,\my) \leq 0, g_2(\mx) \leq 0 \}.
\end{equation}
}{\begin{align}
\mc{F} = \{ \; \mx,\my,\mz \; \big | & \quad h(\mz) - g_0(\mx,\my) \leq 0, \nonumber \\
& \quad g_1(\mx,\my) \leq 0, g_2(\mx) \leq 0 \}.
\end{align}}

@@

\subsection{Stationarity of Limit Points} \label{c-b}
\reviewF{We discuss the convergence of the iterates generated by the iterative algorithm. In order to do that, let us use consider a single global indexing \eqn{t} to represent both \ac{SCA} step \eqn{k} and \ac{AO} index \eqn{i}. It corresponds to every \ac{AO} iterations and \ac{SCA} updates performed within each of the \ac{AO} step.
Using the unified index \eqn{t}, we denote iterate \eqn{\ma^{t}} as a vector stacking all optimization variables produced in every \ac{SCA} iteration \eqn{{k}} and \ac{AO} step \eqn{{i}}.

\review{Using the discussions in Appendices \ref{b_obj} and \ref{mcity}, we can show that the bounded and monotonically decreasing sequence \eqn{\{f(\ma^t)\}} generated by the iterative algorithm converges, using \cite[Prop. A.3]{bertsekas1999nonlinear}. Unfortunately, such a claim cannot be made on the convergence of \eqn{\{\ma^t\}}. However, due to the compactness of feasible set, the sequence of iterates \eqn{\{\ma^t\}} is bounded. Therefore, there exists at least one subsequence that converges to a limit point in the feasible set \cite[Th. 3.6]{rudin1964principles}.}

@@

Let us prove the stationarity of \eqn{\bar{\ma}} by contradiction. Assume that \eqn{\bar{\ma}} is not a stationary point, then there exist some other point \eqn{\ma^\prime \in \{\ma^t\}}, such that \eqn{\nabla f (\bar{\ma})^\tran (\ma^\prime - \bar{\ma}) < 0} and \eqn{f(\bar{\ma}) > f(\ma^\prime)}. Since \eqn{\ma^\prime} is a point in \eqn{\{\ma^t\}}, there exist a subsequence that converges to \eqn{\ma^\prime}, for which \eqn{\ma^\prime} is a limit point. However, from \eqref{limpoint}, we have \eqn{f(\bar{\ma}) = f(\ma^\prime)} for all limit points of \eqn{\{\ma^t\}}, which is a contradiction to our initial assumption.

@@

\review{Before proceeding further, we ensure the convergence of \eqn{\{\hat{f}(\ma^t)\}} by showing that \eqn{\{\hat{f}(\ma^t)\}} is monotonically decreasing in each step \eqn{t}. To do so, let us consider the minimizers \eqn{\mat{t}} and \eqn{\mat{t+1}} of problem \eqref{con-m} in iterations \eqn{{t-1}} and \eqn{{t}}, respectively. Then, by using \eqn{\mat{t}} in the proximal term of \eqref{mod_obj} as \eqn{\|\mat{} - \mat{t}\|^2}, the following inequality holds at every update step \eqn{{t}} as
\begin{equation} \label{mcity_origfunc}
\hat{f}(\mat{t+1}) + \tau^t \|\mat{t+1} - \mat{t} \|^2 \leq \hat{f}(\mat{t})
\end{equation}
where \eqn{\tau^t} is defined as \eqn{\tau_k^{(i)}} in \eqref{mod_obj} and \eqn{\|\mat{t+1} - \mat{t} \|^2 \geq 0}. Therefore, by using \eqref{mcity_origfunc} and Appendix \ref{b_obj}, convergence of \eqn{\{\hat{f}(\ma^t)\}} can be established by using \cite[Prop. A.3]{bertsekas1999nonlinear}.}

@@

Using \eqref{con-sub-set}, we have \eqn{\mc{X}_{k}^{(i)} \subset \mc{F}} and \eqn{\mc{Y}_{k}^{(i)} \subset \mc{F}}, therefore, \eqn{\bar{\ma}} is a feasible point for \eqref{con}. Moreover, the interiors of \eqn{\mc{X}_{k}^{(i)}} and \eqn{\mc{Y}_{k}^{(i)}} are non-empty, therefore, Slater's constraint qualification holds for \eqref{con-m}. Since \eqn{\bar{\ma}} is the solution for \eqref{con-m} as \eqn{k \to \infty,i \to \infty}, there exist Lagrange multipliers \eqn{\mu_i \geq 0} that  satisfies
\begin{equation} \label{kkt_mod_expr}
\textstyle \nabla f(\bar{\ma}) + \mu_0 \big [ \nabla h(\bar{\ma}) - \nabla\hat{g}_0(\bar{\ma};\bar{\ma}) \big ] + \sum_{i=1}^2 \mu_i \nabla g_i(\bar{\ma}) = 0.
\end{equation}
The relation between \eqref{kkt_expr} and \eqref{kkt_mod_expr} is evident by the following facts: (i) The quadratic term in \eqref{mod_obj} \eqn{\|\ma^{t_{j+1}} - \ma^{t_j}\|^2 \to 0}  as \eqn{j \to \infty, \ma^{t_j} \to \bar{\ma}}, since we assume that \eqn{\bar{\ma}} is the limit point of a convergent subsequence \eqn{\{\ma^{t_j}\}}. Therefore, the gradient evaluated at \eqn{\bar{\ma}} satisfies \eqn{\nabla {f}(\bar{\ma}) = \nabla \hat{f}(\bar{\ma})}. (ii) Additionally, by using the continuity of function \eqn{g_o} and \eqref{con-relax}, equivalence between the gradient of \eqref{con-dc} and \eqref{con-dc-m} is obtained as \eqn{\ma^{t_j} \to \bar{\ma}}
\begin{equation} \label{rhs_equiv}
\nabla h(\bar{\ma}) - \nabla \hat{g}_o(\bar{\ma};\bar{\ma}) = \nabla h(\bar{\ma}) - \nabla g_o(\bar{\ma}).
\end{equation}
If follows immediately from \eqref{rhs_equiv} and \eqn{\nabla {f}(\bar{\ma}) = \nabla \hat{f}(\bar{\ma})} in \eqref{kkt_mod_expr} that the limit point \eqn{\bar{\ma}} satisfies \eqref{kkt_expr}. Finally, by following \cite[Thms. 2 and 11]{scutari_1} and \cite[Prop. 3.2]{amir}, we can prove that every limit point of sequence of iterates \eqn{\{\ma^t\}} generated by the iterative algorithm is a stationary point of the problem \eqref{con}.}

>>>>

The following conditions are required to show the convergence of Algorithm \ref{algo-1}, which is used to solve problems \eqref{eqn-6} and \eqref{eqn-mse-1} in an iterative manner.
\begin{itemize}
\item[(a)] Uniqueness of the minimizer in each step
\item[(b)] Objective function should be bounded below
\item[(c)] Feasible set should be compact
\item[(d)] Sequence of objective values should be strictly decreasing
\end{itemize}
Upon satisfying (a)-(d), we can show the convergence of the objective sequence generated by the Algorithm \ref{algo-1}, using \cite[Th. 3.14]{rudin1964principles}. However, it is not  sufficient enough to ensure the convergence of the corresponding sequence of iterates. Therefore, by following the discussions in \cite{marks1978technical,lanckriet2009convergence,scutari_1}, we can only claim that \reviewF{every limit point of the sequence of iterates generated by the iterative method is a stationary point of original nonconvex formulations in \eqref{eqn-6} and \eqref{eqn-mse-1}}.

Before discussing further on the analysis, let us consider a generalized formulation for the problems in \eqref{eqn-6} and \eqref{eqn-mse-1} as
\begin{IEEEeqnarray}{RcL} \label{con} \neqsub
\underset{\mx,\my,\mz}{\text{minimize}} &\quad& \hat{f}(\mx,\my,\mz) \eqsub \label{con-obj} \\
\text{subject to} &\quad& h(\mz) - g_0(\mx,\my) \leq 0 \eqsub \label{con-dc} \\
&\quad& g_1(\mx,\my) \leq 0 \eqsub \label{con-cvx-blk} \\
&\quad& g_2(\mx) \leq 0 \eqsub \label{con-cvx}
\end{IEEEeqnarray}
where \me{g_2} and \me{\hat{f}} are convex, \me{h} is linear, and \me{g_0} and \me{g_1} are convex w.r.t either \me{\mx} or \me{\my}, but not jointly convex on both variables. The constraint \eqref{con-dc} corresponds to either \eqref{eqn-6.2} or \eqref{eqn-mse-1.2} and the constraint \eqref{con-cvx-blk} represents to either  \eqref{eqn-6.3} or \eqref{eqn-mse-1.3} correspondingly. Other convex constraints are handled by \eqref{con-cvx} and the feasible set of \eqref{con} is given by 
\iftoggle{single_column}{
\begin{equation}
\mc{F} = \{ \; \mx,\my,\mz \; \big | h(\mz) - g_0(\mx,\my) \leq 0, g_1(\mx,\my) \leq 0, g_2(\mx) \leq 0 \}.
\end{equation}
}{\begin{align}
\mc{F} = \{ \; \mx,\my,\mz \; \big | & \quad h(\mz) - g_0(\mx,\my) \leq 0, \nonumber \\
& \quad g_1(\mx,\my) \leq 0, g_2(\mx) \leq 0 \}.
\end{align}}

@@

\subsection{Stationarity of Limit Points} \label{c-b}
\reviewF{We discuss the convergence of the iterates generated by the iterative algorithm. In order to do that, let us use consider a single global indexing \eqn{t} to represent both \ac{SCA} step \eqn{k} and \ac{AO} index \eqn{i}. It corresponds to every \ac{AO} iterations and \ac{SCA} updates performed within each of the \ac{AO} step.
Using this unified index \eqn{t}, we denote iterate \eqn{\ma^{t}} as a vector stacking all optimization variables produced in every \ac{SCA} iteration \eqn{{k}} and \ac{AO} step \eqn{{i}}.

\review{By following the discussions in Appendices \ref{b_obj} and \ref{mcity}, the sequence \eqn{\{f(\ma^t)\}} generated by the algorithm is bounded and monotonically decreasing, therefore, by using \cite[Prop. A.3]{bertsekas1999nonlinear}, convergence of the sequence \eqn{\{f(\ma^t)\}} can be ensured. Unfortunately, such a claim cannot be made on the convergence of \eqn{\{\ma^t\}}. However, due to the compactness of feasible set, the sequence of iterates \eqn{\{\ma^t\}} is bounded. Therefore, we can only claim that there exists at least one subsequence that converges to a limit point in the feasible set \cite[Th. 3.6]{rudin1964principles}.}

@@

Let us prove the stationarity of \eqn{\bar{\ma}} by contradiction. Assume that \eqn{\bar{\ma}} is not a stationary point, then there exist some other point \eqn{\ma^\prime \in \{\ma^t\}}, such that \eqn{\nabla f (\bar{\ma})^\tran (\ma^\prime - \bar{\ma}) < 0} and \eqn{f(\bar{\ma}) > f(\ma^\prime)}. Since \eqn{\ma^\prime} is a point in \eqn{\{\ma^t\}}, there exist a subsequence that converges to \eqn{\ma^\prime}, for which \eqn{\ma^\prime} is a limit point. However, by using \eqref{limpoint}, we have \eqn{f(\bar{\ma}) = f(\ma^\prime)} for all limit points of \eqn{\{\ma^t\}}, which is a contradiction to our initial assumption.

@@

\review{Before proceeding further, we ensure the convergence of \eqn{\{\hat{f}(\ma^t)\}} by showing that \eqn{\{\hat{f}(\ma^t)\}} is decreasing in every update and it is bounded. To do so, let us consider the minimizers \eqn{\mat{t}} and \eqn{\mat{t+1}} of problem \eqref{con-m} in iterations \eqn{{t-1}} and \eqn{{t}}, respectively. Since the proximal term in \eqref{mod_obj} is given as \eqn{\|\mat{} - \mat{t}\|^2} for iteration \eqn{t}, the relation between \eqn{\mat{t}} and \eqn{\mat{t+1}} satisfies
\begin{equation} \label{mcity_origfunc}
\hat{f}(\mat{t+1}) + \tau^t \|\mat{t+1} - \mat{t} \|^2 \leq \hat{f}(\mat{t}) + \tau^t \|\mat{t} - \mat{t} \|^2
\end{equation}
where \eqn{\tau^t} denotes \eqn{\tau_k^{(i)}} in \eqref{mod_obj} and \eqn{\|\mat{t+1} - \mat{t} \|^2 \geq 0}. Thus, by extending \eqref{mcity_origfunc} to every update and by using Appendix \ref{b_obj}, convergence of \eqn{\{\hat{f}(\ma^t)\}} can be shown using \cite[Prop. A.3]{bertsekas1999nonlinear}.}

@@

Using \eqref{con-sub-set}, we have \eqn{\mc{X}_{k}^{(i)} \subset \mc{F}} and \eqn{\mc{Y}_{k}^{(i)} \subset \mc{F}}, therefore, \eqn{\bar{\ma}} is a feasible point for \eqref{con}. Moreover, the interiors of \eqn{\mc{X}_{k}^{(i)}} and \eqn{\mc{Y}_{k}^{(i)}} are non-empty, therefore, Slater's constraint qualification holds for \eqref{con-m}. Since \eqn{\bar{\ma}} is the solution for \eqref{con-m} as \eqn{k \to \infty,i \to \infty}, there exist Lagrange multipliers \eqn{\mu_i \geq 0} that  satisfies
\begin{equation} \label{kkt_mod_expr}
\textstyle \nabla f(\bar{\ma}) + \mu_0 \big [ \nabla h(\bar{\ma}) - \nabla\hat{g}_0(\bar{\ma};\bar{\ma}) \big ] + \sum_{i=1}^2 \mu_i \nabla g_i(\bar{\ma}) = 0.
\end{equation}

The relation between \eqref{kkt_expr} and \eqref{kkt_mod_expr} is evident by using following facts: (i) The quadratic term in \eqref{mod_obj} \eqn{\|\ma^{t_{j+1}} - \ma^{t_j}\|^2 \to 0}  as \eqn{j \to \infty, \ma^{t_j} \to \bar{\ma}}, since we assume that \eqn{\bar{\ma}} is the limit point of a convergent subsequence \eqn{\{\ma^{t_j}\}}. Therefore, the gradient evaluated at \eqn{\bar{\ma}} satisfies \eqn{\nabla {f}(\bar{\ma}) = \nabla \hat{f}(\bar{\ma})}. (ii) Additionally, by using the continuity of function \eqn{g_o} and \eqref{con-relax}, equivalence between the gradient of \eqref{con-dc} and \eqref{con-dc-m} is obtained as \eqn{\ma^{t_j} \to \bar{\ma}}
\begin{equation} \label{rhs_equiv}
\nabla h(\bar{\ma}) - \nabla \hat{g}_o(\bar{\ma};\bar{\ma}) = \nabla h(\bar{\ma}) - \nabla g_o(\bar{\ma}).
\end{equation}
Now, by applying the relation \eqref{rhs_equiv} and \eqn{\nabla {f}(\bar{\ma}) = \nabla \hat{f}(\bar{\ma})} in \eqref{kkt_mod_expr}, we can show that the limit point \eqn{\bar{\ma}} satisfies \eqref{kkt_expr}. Finally, by using \cite[Thms. 2 and 11]{scutari_1} and \cite[Prop. 3.2]{amir}, we can show that every limit point of sequence of iterates \eqn{\{\ma^t\}} generated by the iterative algorithm is a stationary point of problem \eqref{con}.}

### 2015-11-22 Report/convergence_distributed.tex
different position for {\hat{f}(x^t)}
updated

\reviewF{Convergence of the primal decomposition and the \ac{ADMM} follow the same discussions as in Appendix \ref{sec-3.5}, if in each \ac{SCA} step, the distributed schemes converge to the centralized solution. To show that, let us consider subproblem \eqref{eqn-decent-1} in the \eqn{\ith{k}} \ac{SCA} step, solved by distributed method using a regularized objective as in \eqref{mod_obj}. At first, the convergence of the primal decomposition method is discussed by using following properties. (i) The feasible set is non-empty and bounded, therefore, each subproblem satisfies the Slater's constraint qualifications. (ii) Due to strong convexity of the objective \eqref{mod_obj} in subproblem, the minimizer is unique. \review{Therefore, by using the above facts, as \eqn{j \to \infty}, the convergence of the primal decomposition can be shown using \cite[Prop. 8.2.6]{bertsekas2003convex} for a diminishing step size in each subgradient update.}}

>>>>

\reviewF{Convergence of the primal decomposition and the \ac{ADMM} follow the same discussions as in Appendix \ref{sec-3.5}, if in each \ac{SCA} step, the distributed schemes converge to the centralized solution. To show that, let us consider subproblem \eqref{eqn-decent-1} in the \eqn{\ith{k}} \ac{SCA} step, solved by distributed method using a regularized objective as in \eqref{mod_obj}. At first, the convergence of the primal decomposition method is discussed by using following properties. (i) The feasible set is non-empty and bounded, therefore, each subproblem satisfies the Slater's constraint qualifications. (ii) Due to strong convexity of the objective \eqref{mod_obj} in subproblem, the minimizer is unique. \review{Therefore, by using the above facts and as \eqn{j \to \infty}, the convergence of the primal decomposition method follows \cite[Prop. 8.2.6]{bertsekas2003convex} by using diminishing step size in each subgradient update.}}

### 2015-11-22 Report/dual_approach.tex
updated

\reviewF{Assuming that the following conditions are satisfied by the distributed schemes in every \ac{SCA} step, \textit{i.e.}, (i) by ensuring the uniqueness of the minimizer, and (ii) by choosing \eqn{J_{\max}} to be sufficiently large enough to ensure strict monotonicity of the objective, convergence of the distributed algorithms follow the discussions presented in Appendices \ref{sec-3.5} and \ref{sec-dist-conv}. Moreover, if the receivers are updated together with the transmit precoders as in Algorithm \ref{algo-3}, strict monotonic decrease of the objective sequence can still be ensured. The reason is that the \ac{MMSE} receiver is optimal for the fixed transmit precoders obtained after each \ac{SCA} update. However, in practice, to reduce the amount of information exchange among the coupling \acp{BS}, often distributed schemes are iterated for few number of iterations, say, for \eqn{J_{\max}} only. In such a case, the convergence of the sequence of iterates generated by the distributed algorithm cannot not be ensured, since it is difficult to show the monotonicity of objective in each \ac{SCA} step. It follows from the fact that in each primal or \ac{ADMM} update, the global objective cannot be guaranteed to decrease monotonically.}

>>>>

\reviewF{Assuming that the following conditions are satisfied by the distributed schemes in every \ac{SCA} step, \textit{i.e.}, (i) by ensuring the uniqueness of the minimizer, and (ii) the distributed methods are performed for \eqn{j \to \infty}, convergence analysis follow the discussions in Appendices \ref{sec-3.5} and \ref{sec-dist-conv}. Moreover, the convergence discussions in Appendices \ref{sec-3.5} and \ref{sec-dist-conv} are valid even if the receivers are updated together with the transmit precoders as in Algorithm \ref{algo-3}, since strict monotonic decrease of the objective sequence can still be ensured. The reason is that the \ac{MMSE} receiver is optimal for the fixed transmit precoders obtained after each \ac{SCA} update. However, in practice, to reduce the amount of information exchange among the coupling \acp{BS}, often distributed schemes are iterated for limited number of iterations, say, for \eqn{J_{\max}} only. In such a case, convergence of the distributed algorithms cannot not be ensured, since it is difficult to show that the objective value is monotonically decreasing at every \ac{SCA} step. It follows from the fact that in each primal or \ac{ADMM} update, the global objective cannot be guaranteed to decrease monotonically.}

### 2015-11-22 Response/Response 3/additions.tex
updated

\begin{enumerate}
	\item We have rewritten Appendix A-D to discuss the stationarity of limit points of the sequence of beamformer iterates generated by the centralized algorithms.
	\item We have updated the convergence of distributed algorithm to reflect the same.
\end{enumerate}

@@

Finally, to discuss the convergence of the sequence of iterates generated by the centralized scheme in Algorithm 1, we use an unified superscript index \eqn{t} to represent both \ac{AO} index \eqn{i} and \ac{SCA} indexing \eqn{k}. By doing so, we represent iterate \eqn{\mbf{x}^{t}} as the solution variable produced by the iterative algorithm in every \ac{SCA} \eqn{k} and \ac{AO} step {i}. Using this notation, we have revised our convergence discussions in Appendices A-C and A-D.

>>>>

In summary, the revised manuscript includes the following changes.
\begin{enumerate}
	\item We have rewritten Appendix A-D to discuss the stationarity of limit points of the sequence of beamformer iterates generated by the centralized algorithms.
	\item We have updated the convergence of distributed algorithm to reflect the same.
\end{enumerate}

@@

\vspace{1eM}
In order to discuss the convergence of the sequence of iterates generated by the centralized scheme in Algorithm 1, we use an unified superscript index \eqn{t} to represent both \ac{AO} index \eqn{i} and \ac{SCA} indexing \eqn{k}. By doing so, we represent iterate \eqn{\mbf{x}^{t}} as the solution variable produced by the iterative algorithm in every \ac{SCA} \eqn{k} and \ac{AO} step {i}. Using this notation, we have revised our convergence discussions in Appendices A-C and A-D.
